### 2017-06-13 R/NHTS.Rmd
Trying to incorporate MSA names
Having difficulty.  It's not working yet.
Created msa2.R
This is a temporary name.  This script creates the active transport mean list by MSA.  msa.Rmd creates the list for F, the population

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("tidyverse")
library("devtools")
#library("reshape2")
#library("plyr")
#library("dplyr")
library("TravelSurvey")
library("ITHIM")
fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```

@@

PERV2PUB <- read.csv(file = "~/GHI/data/NHTS/Ascii/PERV2PUB.CSV", na.strings = "-9")
names(PERV2PUB) <- c("HOUSEID","PERSONID","VARSTRAT","WTPERFIN","SFWGT","HH_HISP","HH_RACE","DRVRCNT","HHFAMINC","HHSIZE","HHVEHCNT","NUMADLT","WRKCOUNT","FLAG100","LIF_CYC","CNTTDTR","BORNINUS","CARRODE","CDIVMSAR","CENSUS_D","CENSUS_R","CONDNIGH","CONDPUB","CONDRIDE","CONDRIVE","CONDSPEC","CONDTAX","CONDTRAV","DELIVER","DIARY","DISTTOSC","DRIVER","DTACDT","DTCONJ","DTCOST","DTRAGE","DTRAN","DTWALK","EDUC","EVERDROV","FLEXTIME","FMSCSIZE","FRSTHM","FXDWKPL","GCDWORK","GRADE","GT1JBLWK","HHRESP","HHSTATE","HHSTFIPS","ISSUE","OCCAT","LSTTRDAY","MCUSED","MEDCOND","MEDCOND6","MOROFTEN","MSACAT","MSASIZE","NBIKETRP","NWALKTRP","OUTCNTRY","OUTOFTWN","PAYPROF","PRMACT","PROXY","PTUSED","PURCHASE","R_AGE","R_RELAT","R_SEX","RAIL","SAMEPLC","SCHCARE","SCHCRIM","SCHDIST","SCHSPD","SCHTRAF","SCHTRN1","SCHTRN2","SCHTYP","SCHWTHR","SELF_EMP","TIMETOSC","TIMETOWK","TOSCSIZE","TRAVDAY","URBAN","URBANSIZE","URBRUR","USEINTST","USEPUBTR","WEBUSE","WKFMHMXX","WKFTPT","WKRMHM","WKSTFIPS","WORKER","WRKTIME","WRKTRANS","YEARMILE","YRMLCAP","YRTOUS","DISTTOWK","TDAYDATE","HOMEOWN","HOMETYPE","HBHUR","HTRESDN","HTHTNRNT","HTPPOPDN","HTEEMPDN","HBRESDN","HBHTNRNT","HBPPOPDN","HH_CBSA","HHC_MSA")

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(ITHIM:::convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               # HHS = as.character(convertToHHS(as.character(HHSTATE))),
                               MSA_ID = HHC_MSA, stringsAsFactors = FALSE)
})

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
rm(list=ls())
#install.packages(c("ggplot2","dplyr","openssl","httr", "git2r", "devtools", "roxygen2"))
library("tidyverse")
library("devtools")
#library("reshape2")
#library("plyr")
#library("dplyr")
library("TravelSurvey")
library("ITHIM")
fig.width <- 6 # inches
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```

@@

PERV2PUB <- read.csv(file = "~/GHI/data/NHTS/Ascii/PERV2PUB.CSV", na.strings = "-9", stringsAsFactors = FALSE)
names(PERV2PUB) <- c("HOUSEID","PERSONID","VARSTRAT","WTPERFIN","SFWGT","HH_HISP","HH_RACE","DRVRCNT","HHFAMINC","HHSIZE","HHVEHCNT","NUMADLT","WRKCOUNT","FLAG100","LIF_CYC","CNTTDTR","BORNINUS","CARRODE","CDIVMSAR","CENSUS_D","CENSUS_R","CONDNIGH","CONDPUB","CONDRIDE","CONDRIVE","CONDSPEC","CONDTAX","CONDTRAV","DELIVER","DIARY","DISTTOSC","DRIVER","DTACDT","DTCONJ","DTCOST","DTRAGE","DTRAN","DTWALK","EDUC","EVERDROV","FLEXTIME","FMSCSIZE","FRSTHM","FXDWKPL","GCDWORK","GRADE","GT1JBLWK","HHRESP","HHSTATE","HHSTFIPS","ISSUE","OCCAT","LSTTRDAY","MCUSED","MEDCOND","MEDCOND6","MOROFTEN","MSACAT","MSASIZE","NBIKETRP","NWALKTRP","OUTCNTRY","OUTOFTWN","PAYPROF","PRMACT","PROXY","PTUSED","PURCHASE","R_AGE","R_RELAT","R_SEX","RAIL","SAMEPLC","SCHCARE","SCHCRIM","SCHDIST","SCHSPD","SCHTRAF","SCHTRN1","SCHTRN2","SCHTYP","SCHWTHR","SELF_EMP","TIMETOSC","TIMETOWK","TOSCSIZE","TRAVDAY","URBAN","URBANSIZE","URBRUR","USEINTST","USEPUBTR","WEBUSE","WKFMHMXX","WKFTPT","WKRMHM","WKSTFIPS","WORKER","WRKTIME","WRKTRANS","YEARMILE","YRMLCAP","YRTOUS","DISTTOWK","TDAYDATE","HOMEOWN","HOMETYPE","HBHUR","HTRESDN","HTHTNRNT","HTPPOPDN","HTEEMPDN","HBRESDN","HBHTNRNT","HBPPOPDN","HH_CBSA","HHC_MSA")

NHTS.person <- with(PERV2PUB,{
                    data.frame(HOUSEID = HOUSEID,
                               PERSONID = PERSONID,
                               SEX = as.factor(ifelse(R_SEX=="1", "M", ifelse(R_SEX=="2", "F", NA))),
                               AGE = as.factor(ITHIM:::convertToAgeClass(R_AGE)),
                               MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                               HHSTATE = as.character(HHSTATE),
                               # HHS = as.character(convertToHHS(as.character(HHSTATE))),
                               MSA_ID = as.character(as.integer(HHC_MSA)), stringsAsFactors = FALSE)
})

### 2017-06-13 R/TravelSurvey.Rmd
Created msa2.R
This is a temporary name.  This script creates the active transport mean list by MSA.  msa.Rmd creates the list for F, the population

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
library("tidyverse")
library("ITHIM")
library("TravelSurvey")
```

@@

```{r TravelSurvey, eval = TRUE, fig.width = fig.width, echo = FALSE}
NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    id <- paste0(houseID,"-",subjectID)
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
    location <- location #msaname[location]
})
```

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
rm(list=ls())
library("tidyverse")
library("ITHIM")
library("TravelSurvey")
```

@@

```{r TravelSurvey, eval = TRUE, fig.width = fig.width, echo = FALSE}
NHTS.ts <- readRDS(file = "~/GHI/R/data/NHTS.TravelSurvey.rds")
NHTS.df <- dplyr::left_join(NHTS.ts@person, NHTS.ts@trip, by = c("houseID","subjectID"))
NHTS.df <- within(NHTS.df, {
    id <- paste0(houseID,"-",subjectID)
    duration <- ifelse(is.na(duration), 0, duration)
    mode <- factor(mode, levels = c("walk","cycle","other"))
    location <- location
})
saveRDS(NHTS.df, file = "~/GHI/R/data/NHTS.df.rds")
```

### 2017-06-13 R/msa.Rmd
Created msa2.R
This is a temporary name.  This script creates the active transport mean list by MSA.  msa.Rmd creates the list for F, the population

foo <- read.csv(file="~/GHI/data/join2.csv", stringsAsFactors = FALSE)

msaTest <- 6442

msaMatrix <- foo %>% filter(msaNHTS == msaTest) %>%
select(stateFIPS,countyFIPS)

getPopulation(state=msaMatrix$stateFIPS, county =
msaMatrix$countyFIPS)

>>>>

# MSA Population Size (F)

```{r msalibs, eval = TRUE, echo = TRUE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
rm(list=ls())
library("devtools")
#install_github("ITHIM/ITHIM", ref="devel")
install("~/ITHIM/")
library("ITHIM")
```
## List of Population Size Matrices

```{r msamsa, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
msaIDFile <- read.csv(system.file("join2.csv", package = "ITHIM"), stringsAsFactors = FALSE)
msaIDs <- msaIDFile$msaNHTS %>% unique
msaIDs <- msaIDs[!is.na(msaIDs)] %>% as.list
names(msaIDs) <- msaIDs
populationList <- getPopulation(msaIDs)

length(populationList)
names(populationList)
head(populationList, 3)

saveRDS(populationList, file = "~/GHI/R/data/populationList.rds")
```

## Top Three MSAs

Let's inspect the top three MSAs by population size.

```{r msa2, eval = TRUE, echo = TRUE, warning = FALSE, error = FALSE, message = FALSE}
totalPop <- lapply(populationList,sum) %>% unlist
totalPop[totalPop %>% order(., decreasing = TRUE)] %>% head(., 3)
msaIDFile %>% filter(msaNHTS %in% c(4472,5602,1602)) %>% select(msaName,msaNHTS) %>% unique
```

It's L.A. New York and Chicago.  Seems right.

Notice the non-uniqueness of `msaNHTS` in the data.
